---
title: "Sample Report"
subtitle: "An Analysis of Survey Data"
author: 
  - Hung Vo
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: |
  This is a summary of the report.
mainfont: 'Arial Narrow'
output: 
  word_document:
    fig_caption: true
    reference_docx: './style/business-report-style.docx'
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# load packages
library(tidyverse)
library(readr)
library(flextable)

# read in City of Casey short survey
casey_survey_raw <- readr::read_csv(file = "./data/casey-next-data-short-survey.csv",
                                    col_names = TRUE) %>% 
  `colnames<-`(make.names(names(.))) %>% 
  rename("Age.Group" = "What.is.your.age.",
         "Gender" = "What.is.your.Gender") %>% 
  mutate(Age.Group = dplyr::recode(replace_na(tools::toTitleCase(tolower(Age.Group)), "Not Specified"),
                                   "Unk" = "Unknown",
                                   "49-68" = "Unknown", # one observation only
                                   "Unkown" = "Unknown"),
         Gender = dplyr::recode(replace_na(tools::toTitleCase(tolower(Gender)), "Not Specified"),
                                "Unk" = "Unknown",
                                "Unkown" = "Unknown",
                                "m" = "Male",
                                "Perfer not to Say" = "Prefer not to Say"))
```

###### Pagebreak

# Executive Summary

An executive summary.

# Methodology

## Data Sources

Details about the data sources.

## Analyses

Details about the analytical techniques used.

## Limitations

Any limitations.

###### Pagebreak

# Key Findings

## Respondent demographic characteristics

Over half of the respondents were female. Almost a quarter of the survey respondents were aged between 29 and 38 years of age.

```{r deomgraphics_tbl, echo=FALSE, warning=FALSE}

# page width of the word document
body_p_w <- 6.69291 # 17 cm into inches to fit the table

# summarise by characteristic
demographics_df <- c("Age.Group", 
                     "Gender") %>% 
  purrr::map( ~ casey_survey_raw %>% 
                select(.x) %>% 
                rename("Group" = !!sym(.x)) %>% 
                group_by(Group) %>% 
                count(.) %>% 
                mutate(Characteristic = .x) %>% 
                dplyr::select(Characteristic, everything())) %>% 
  reduce(rbind) %>% 
  group_by(Characteristic) %>% 
  mutate(n.perc = scales::percent(n / sum(n)))

# render a table 
ft_demographics <- flextable(demographics_df)
ft_demographics <- width(ft_demographics, j = ~ Characteristic, width = 0.4 * body_p_w)
ft_demographics <- width(ft_demographics, j = ~ Group, width = 0.4 * body_p_w)
ft_demographics <- width(ft_demographics, j = ~ n, width = 0.1 * body_p_w)
ft_demographics <- width(ft_demographics, j = ~ n.perc, width = 0.1 * body_p_w)
ft_demographics <- merge_v(ft_demographics, j = ~ Characteristic)
ft_demographics <- theme_vanilla(ft_demographics)
ft_demographics <- set_header_labels(ft_demographics,
                                     n.perc = "% of Total")
ft_demographics <- align(ft_demographics, align = "left")
ft_demographics <- align(ft_demographics, align = "left", part = "header")
ft_demographics

```

###### Pagebreak

## Term frequencies for City of Casey Vision

"safe" was the highest recorded word by survey respondents regarding the item - "*What three words would you use to describe your Vision for the City of Casey?*".

```{r term_freq, echo=FALSE, warning=FALSE, fig.width=6.69291, fig.height=7, dpi=300}

# summarise term frequencies
term_freq_df <- casey_survey_raw %>% 
  dplyr::select(3:5) %>%
  `colnames<-`(make.names(as.character(unlist(.[1,])))) %>% 
  filter(row_number() != 1) %>% 
  tidyr::gather() %>% 
  filter(!is.na(value)) %>% 
  mutate(value = tolower(stringi::stri_trans_general(value, "latin-ascii"))) %>% 
  group_by(value) %>% 
  count() %>% 
  arrange(desc(n)) %>% 
  dplyr::rename("Term" = "value",
                "Frequency" = "n") 

# plot the frequencies
ggplot(data = head(term_freq_df, 20),
       aes(x = reorder(Term, Frequency),
           y = Frequency)) +
  geom_bar(stat = "identity",
           fill = "lightblue",
           width = 0.5) +
  theme_classic() +
  coord_flip() +
  geom_text(aes(x = Term, y = Frequency, label = Frequency), size = 3, vjust = 0.5, hjust = -0.25) +
  ylab("Frequency") +
  xlab("Term") +
  labs(title = "Top 20 commonly used words for describing the\nVision for the City of Casey",
       caption = paste0("n=", scales::comma(nrow(term_freq_df)), " words recorded by survey respondents"))

```

